Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-05-07 paper/response.tex

\begin{item}
\textbf{How the model can incorporate the interactions among pedestrians (i.e
group motion) and the influences from neighbouring pedestrians (for
instances such as collision avoidance)?}
\end{item}

Thank you for this insightful question. 
Since the focus of this paper was on developing a method to generate predictions at real-time for the autonomous vehicle context, we did not consider the effect of incorporating interactions between predictions. 
However, social forces are a natural avenue for future work, and so we included the following paragraph in the paper:

\response{Though including social forces into the model is outside of the scope of this paper, its incorporation could begin as follows.  
In the current motion model with a single vector field, the acceleration of the $i$th agent is given by $\ddot{x}_i = s^2 DX(x_i) \cdot X(x_i)$.  
Incorporating a social force $F_{i}$ acting on the $i$th agent can be done by instead asserting $\ddot{x}_i = s^2 DX(x) \cdot X(x) + F_i$.  
Usually $F_{i} = \sum_{j} \nabla U( x_j - x_i)$ where $U$ is an interaction potential \cite{Helbing1995}. 
The algorithms for generating real-time prediction would then generalize to this new vector-field definition.
}

\begin{item}
\textbf{Presentation and organisation
The motivation behind choosing start/end points based clustering is not
clear. Does clustering based on start/end points help to identify
different motion models? Isn't it better to cluster considering the
entire trajectory? }
\end{item}

Thank you for this relevant question.
As stated in \cite{Morris2009}, the choice of clustering technique is not nearly as important as the distance metric. 
Our success with distance functions that took a whole trajectory was limited on the data we tested and we found more success using a custom distance metric that only considered the start and end points of a trajectory as we describe in Comment \ref{distmetric} to Reviewer 1. 
We have several hypotheses as to why this is true.  
For one, the spatial scale of the data we test against showcases important features (e.g. curb cuts and storefronts), which lead to clustered start points and end points. 
Similarly, we tested against high quality data in which trajectories with irreconcilable occlusions were rare and thus could be omitted.

\begin{item}
\textbf{Do you cluster different scenes provided in campus dataset \cite{Alahi2016} (i.e
Valley, Fangron) separately or all together? When motion models are
learnt, are they learnt in scene specific manner or altogether?}
\end{item}

Thank you for noticing that this is unclear. 
Our algorithm trains on each scene independently, so clustering, vector field learning, and learning the potential functions are all done for each scene separately. 
To make this more clear, we added the following text to the paper:

@@

\reversemarginpar\marginnote{\#4.8}
\response{An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time t, and the X is the end of the trajectory. The likelihood of detection is depicted using the virdis color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} suffer from the inability of their motion model to adequately match the speed of the agent. The algorithm from \cite{Alahi2016} quickly passes beyond the boundaries of the scene, so the plots are ommitted here.
}

\end{item}

\end{enumerate}

\section*{Reviewer 5}
\begin{enumerate}
\begin{item}
\textbf{
It would be more interesting if the authors show whether
the prediction algorithm would transfer the learned ``knowledge" of
forecasting in novel scenes.}

@@

Thank you for your comment. 
Though this was not the focus of this paper, the low-dimensional parameterization of the vector fields make transfer learning more amenable. 
As it is, this is as an immediate avenue for future work which we describe in the following addition to the text: 
\response{We also hope to do transfer learning \Ram{I flipped the previous two words.} with this model using scene segmentation from \cite{Walker2014}, as well as the semantic context descriptors and routing scores from \cite{Ballan2016} to show how vector fields can be transferred to novel scenes. It appears that the low-order parameterization of our model, and unit-length vector field assumption make it particularly amenable to the methods developed in \cite{Ballan2016}.}

\end{item}
\begin{item}
\textbf{
More statistically result is expected
rather than analyzing ``four different scenes", and comparing run-time
by "averaged across several agents and scenes" (how many?).}

### 2017-05-08 paper/response.tex

\documentclass[usenames,dvipsnames]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[letterpaper, total={6in, 8in}]{geometry}
\usepackage{color}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{marginnote}

\newcommand{\todo}[1]{\textcolor{red}{#1}}
\newcommand{\Ram}[1]{{\normalsize{\textbf{({\color{green}Ram:\ }#1)}}}}
\providecommand{\response}[1]{
\noindent
\noindent\colorbox{gray!20}{
\parbox{\textwidth}{
\setlength{\parskip}{.1in}
\setlength{\parindent}{.1in}
#1}
}
}

\title{\LARGE Real-Time Certified Probabilistic Pedestrian Forecasting \\ \textbf{Author's Response} }

\author{Henry O. Jacobs, Owen K. Hughes, \\ Matt Johnson-Roberson, and Ram Vasudevan }

@@

Thank you for the positive assessment.
\end{item}

\begin{item} \label{newmetrics}
\textbf{With the current form of the results it is hard to compare the
improvements in terms of accuracy gained. This can be overcome by
including results such as physical distance between predicted paths and
ground truth observations. Such matrices are provided in the baseline
models \cite{Kitani2012} \cite{Karasev2016} \cite{Robicquet2016} with accuracy values in meters. }

Thank you for the suggestion. 
The objective of this paper was to develop a predictor that would be effective for use in the autonomous vehicle context. 
In this instance, to ensure safety it is critical that the generated set of predictions contains the ground-truth observed trajectory while including as few false positive detections as possible.
Since the ROC curve plots the true positive rate (i.e. the proportion of the ground truth trajectory that is correctly identified) against the false positive rate (i.e. the proportion of the generated set that does not correspond to the ground truth trajectory), it evaluates this aforementioned safety criteria for autonomous vehicles exactly.

On the other hand the Modified Hausdorff Distance (MHD) from \cite{Dubuisson1994} measures the average geometric distance between the ground-truth observed trajectory and the generated set of predictions. 
Though popular in evaluating the geometric proximity of the ground truth trajectory and a predicted set, it is not the most appropriate way to evaluate the utility of an algorithm in the autonomous vehicle context. 
Specifically consider the instance of a generated set of predictions which does not contain the ground-truth observed trajectory but is close to the ground-truth trajectory geometrically. 
If this generated set of predictions was used in the autonomous vehicle context, it would not preclude certain portions of the space where the person was occupying. 
Notice that In this instance the true positive rate would be zero meaning that the generated set of predictions was not useful.
Whereas the MHD would describe this generated set of predictions as informative.

Nevertheless, we addressed this concern by adding a comparison to the MHD which is summarized in the Figure \ref{MHD} below and included in the resubmitted version of our manuscript. We outperform \cite{Kitani2012} and \cite{Alahi2016} in the intermediate term, but at short times \cite{Alahi2016} puts more weight on the direction of the observed trajectory, and so their narrow distribution is closer to the trajectory. At large scales, \cite{Kitani2012} outperforms us because they know the endpoint of the trajectory. If you look at Figure \ref{bookstore} and \ref{death}, you'll see that while they are geometrically closer to the observed trajectory, they don't include it.
%\Ram{it would be useful if we summarized what we were seeing the MHD plot here. Meaning it would be helpful if you could say something to the effect that with respect to MHD we are good in the medium term. In addition it would be nice if we could see some sample trajectories from lstm to really illustrate that they aren't including the ground truth trajectory but are just close geometrically which contributes to their low MHD score. That image should be included in the resubmitted text and in this response letter}
We have included the following passage to explain both metrics in the revised submission:

@@

\end{item}
\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{figures/mhd_results.eps}
	\caption{A comparison of the Modified Hausdorff Distance from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. At longer timescales the MHD to the trajectory of most algorithms converges. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms which assume that the end point of the trajectory is unknown.}
   \reversemarginpar\marginnote{\#4.10}
	\label{MHD}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{figures/the_results.eps}
	\caption{A comparison of the AUC of the various algorithms. Note that the initial dip in the performance of \cite{Kitani2012} is due to their confidence in their initial estimate. We sampled the S-LSTM \cite{Alahi2016} model $100$ times in order to organically extract a less concentrated probability distribution from their algorithm, but their confidence combined with the over-reliance on social forces at moderate-to-large timescales lowered their performance.}
	\reversemarginpar\marginnote{\#4.9}
	\label{AUC}
\end{figure}

\begin{item}
\textbf{How the model can incorporate the interactions among pedestrians (i.e
group motion) and the influences from neighbouring pedestrians (for
instances such as collision avoidance)?}
\end{item}

Thank you for this insightful question. 
Since the focus of this paper was on developing a method to generate predictions at real-time for the autonomous vehicle context, we did not consider the effect of incorporating interactions between predictions. 
However, social forces are a natural avenue for future work, and so we included the following paragraph in the paper:

@@

Thank you for noticing that this is unclear. 
Our algorithm trains on each scene independently, so clustering, vector field learning, and learning the potential functions are all done for each scene separately. 
To make this more clear, we added the following text to the paper:

\reversemarginpar\marginnote{\#4.3}
\response{We did a 2-fold cross validation by using 20\% of the data for testing and the remainder for training within each scene. 
We learned separate collections of vector fields and model parameters for each fold on all of the four scenes on which we tested.}

\begin{item} \label{distmetric}
\textbf{The motivation behind choosing the affinity propagation clustering algorithm is not clearly stated. 
What is the distance measure used (i.e Euclidian) ? 
Not specifying such information makes reproduction of this work not feasible. }

This was an oversight on our part, thank you for noticing it. 
The distance used is a custom distance function. Let one trajectory $A$ start at $(x_{A,\mathrm{start}}, y_{A,\mathrm{start}})$ and end at  $(x_{A,\mathrm{end}}, y_{A,\mathrm{end}})$, and another trajectory $B$ start at $(x_{B,\mathrm{start}}, y_{B,\mathrm{start}})$ and end at $(x_{B,\mathrm{end}}, y_{B,\mathrm{end}})$ . 
We define the points $\mathbf{a}_1 = (x_{A, \mathrm{start}}, y_{A, \mathrm{start}}, x_{A, \mathrm{end}}, y_{A, \mathrm{end}})$, $\mathbf{a}_2 = (x_{A, \mathrm{end}}, y_{A, \mathrm{end}}, x_{A, \mathrm{start}}, y_{A, \mathrm{start}})$, and $\mathbf{b} = (x_{B, \mathrm{start}}, y_{B, \mathrm{start}}, x_{B, \mathrm{end}}, y_{B, \mathrm{end}})$. 
We then define our distance measure as $d(A, B) :=  \min \left\{ d_e(\mathbf{a}_1, \mathbf{b}), d_e(\mathbf{a}_2, \mathbf{b}) \right\}$, for the euclidean distance $d_e$ in $\mathbb{R}^4$.  This is designed such that transposing endpoints of a trajectory doesn't matter, and so a trajectory that starts at point A and ends at point B is close to a trajectory that starts at point B and ends at point A.  
We have included the following clarification:

\reversemarginpar\marginnote{\#4.2}
\response{
	We then cluster in $\mathbb{R}^4$ using Affinity Propagation \cite{FreyDueck2007} and a custom distance measure defined on the endpoints of trajectories. 
	Let one trajectory $A$ start at $(x_{A,\mathrm{start}}, y_{A,\mathrm{start}})$ and end at  $(x_{A,\mathrm{end}}, y_{A,\mathrm{end}})$, and another trajectory $B$ start at $(x_{B,\mathrm{start}}, y_{B,\mathrm{start}})$ and end at $(x_{B,\mathrm{end}}, y_{B,\mathrm{end}})$ . 
	We define the points $\mathbf{a}_1 = (x_{A, \mathrm{start}}, y_{A, \mathrm{start}}, x_{A, \mathrm{end}}, y_{A, \mathrm{end}})$, $\mathbf{a}_2 = (x_{A, \mathrm{end}}, y_{A, \mathrm{end}}, x_{A, \mathrm{start}}, y_{A, \mathrm{start}})$, and $\mathbf{b} = (x_{B, \mathrm{start}}, y_{B, \mathrm{start}}, x_{B, \mathrm{end}}, y_{B, \mathrm{end}})$. 
	We then define our distance measure as $d(A, B) :=  \min \left\{ d_e(\mathbf{a}_1, \mathbf{b}), d_e(\mathbf{a}_2, \mathbf{b}) \right\}$, for the euclidean distance $d_e$ in $\mathbb{R}^4$. 
	This function measures the distance between the endpoints irrespective of their ordering, which means that a trajectory that starts from point A and ends at point B will be close to a trajectory that starts from point B and ends at point A.
	The scale of the datasets we tested on had large enough spatial scale that clustering based on endpoints captured people moving from destination to destination, e.g. from a storefront to the sidewalk at the edge of a scene. On this dataset, distance functions that utilize the entire trajectory such as DTW, LCSS, and PF from \cite{Morris2009} and TRACLUS from \cite{Lee2007} did not identify pedestrian intent as well as our method did. While it is unclear why TRACLUS underperformed on our data, PF, DTW, and LCSS appeared to put trajectories that were very similar for periods of time together even though they had very different intents.}

@@

Thank you for this criticism. 
We hope we adequately addressed it by strengthening the description of our method for learning the motion model, as well as quantifying the way that we tested our data as is described in our responses to the suggestions by other reviewers.

\end{item}

\begin{item}
\textbf{
Need to use and apply more deep learning approaches such as social LSTM
or other machine methods.}

Thank you for the suggestion. 
We hope that we have addressed it by including a review of literature of social motivated models, including S-LSTM, as well as a section on how social factors can be integrated into our model. 
In addition, we compared our approach against S-LSTM in addition to the method proposed in \cite{Kitani2012}. 
We included the visualizations in Figures \ref{bookstore} and \ref{death} below, also which are also updated in the paper.

\reversemarginpar\marginnote{\#4.8}

\begin{figure}
	\centering
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Our Algorithm}   }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/ours_1_2_t=50.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/ours_1_2_t=130.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/ours_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Kitani et al.}  }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=50.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=130.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{S-LSTM} }  
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/lstm_1_2_t=100.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/lstm_1_2_t=300.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/lstm_1_2_t=360.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Random Walk} }  
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=50.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=130.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.2cm}
	\hspace{.5cm}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 1.66s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 4.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 12.33s$
	\end{minipage}

	\caption{
		An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time t, and the X is the end of the trajectory. The likelihood of detection is depicted using the virdis color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in [7] suffer from the inability of their motion model to adequately match the speed of the agent. The algorithm in [13] is confident and close to the trajectory at small times, but their lack of a motion model causes their prediction to compress into a point at intermediate time scales.}
	\label{bookstore}
\end{figure}

\begin{figure}
	\centering
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Our Algorithm}}   
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/ours_death_1_2_t=70.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/ours_death_1_2_t=250.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/ours_death_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Kitani et al.}} 
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/kit_death_1_2_t=70.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/kit_death_1_2_t=250.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/kit_death_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{S-LSTM}} 
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/lstm_1_2_t=100.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/lstm_1_2_t=300.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/lstm_1_2_t=380.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Random Walk} }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=70.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=250.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.2cm}
	\hspace{.5cm}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 2.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 8.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 12.33s$
	\end{minipage}

	\caption{An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time t, and the X is the end of the trajectory. The likelihood of detection is depicted using the virdis color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in [7] are unable to match the speed of the agent and choose the wrong direction to follow the agent around the circle. The algorithm in [13] is confident and close to the trajectory at small times, but their lack of a motion model causes their prediction to compress into a point at intermediate time scales.}
	\label{death}
\end{figure}

@@

\end{item}

\end{enumerate}

\section*{Reviewer 5}
\begin{enumerate}
\begin{item}
\textbf{
It would be more interesting if the authors show whether
the prediction algorithm would transfer the learned "knowledge" of
forecasting in novel scenes.}

### 2017-05-08 paper/response.tex

Thank you for your comment. 
Though this was not the focus of this paper, the low-dimensional parameterization of the vector fields make transfer learning more amenable. 
As it is, this is as an immediate avenue for future work which we describe in the following addition to the text: 
\response{We also hope to do transfer learning with this model using scene segmentation from \cite{Walker2014}, as well as the semantic context descriptors and routing scores from \cite{Ballan2016} to show how vector fields can be transferred to novel scenes. It appears that the low-order parameterization of our model, and unit-length vector field assumption make it particularly amenable to the methods developed in \cite{Ballan2016}.}
